\chapter{Introduction}\label{ch:introduction}

Since the Industrial Revolution, the industry has been evolving, increasing the number of machines in factories in order to satisfy the production demands and to reduce the effort made by the workers. However, in the last few years, the industry motto has been changing, influenced by the development of the technology. The main goal is to decrease the number of people working in firms, reducing, thus, the cost of manpower, while increasing the number of autonomous machines. These mechanisms are able to work without breaks for long periods with a high level of accuracy. 

For instance, nowadays robot arms are one of the most used tools in factories around the world because they are able to perform precise and/or dangerous tasks without making any mistakes. This mechanical arm is divided in diferent parts with similar functions to a human one. The desired rotation and translation motion are achieved based on joints which are the ones responsible for the connection between the links. 

With the above background in mind, the objective of this project is to build figures with lego blocks which represent the Simpson characters. In order to reach the goal, it was necessary to implement a system with two main items: a camera and a robot (ADEPT Cobra). The camera was responsible for taking pictures which were submited to a computation process based on colour and edge detection. With a view to decrease the execution time of the process, the background was subtracted from the images with bricks and then, the outcome was cropped. Hence, it was possible to perform a quick analysis of all images and, consequently, optimize the entire program.

After transforming the coordinates and using the information provided by the camera, it was achievable to move the robot and pick the blocks. The robot is given the final position of its gripper, but needs to calculate the optimal values of its joints to go to the desired location. This procedure is referred as inverse kinematics.

